Machines are Among Us

### 2020-12-02 paper/main.tex
Added some information to README and updated paper

At the end of voting, we calculate a ``crew score''. This score is simply the
maximum vote-off score that any imposter recieved, where votes
are averaged across all agents. Clearly, the imposters would like to minimize the
votes on themselves, so their loss function for training purposes is
simply the crew score. Inversely, the crew's loss function is the negation of
the crew score.
\textbf{Zach: Relate back to GANs, zero-sum game so that adversarial works}
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
Imposter/Crew two different models, multitude of different hyperparameters and
sizes of inputs/outputs.
\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. GANs are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

>>>>

At the end of voting, we calculate a ``crew score''. This score is simply the
maximum vote-off score that any imposter recieved, where votes
are averaged across all agents. Clearly, the imposters would like to minimize the
votes on themselves, so their loss function for training purposes is
simply the crew score. Inversely, the crew's loss function is the negation of
the crew score. This takes the form of a zero-sum game with similar application
as in generative adversarial networks.
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
Imposter/Crew two different models, multitude of different hyperparameters and
sizes of inputs/outputs.
\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search. As discussed previously, to help speed up training time
and reduce gradient overlap between multiple different models training over the
same dataset, we had to only train either one imposter or crew, and keep the rest constant.
This limits the quick adaptivity, and may lead to the models attempting to train
against the constant tcooperative models ratrher than against the adversarial model.

Furthermore, the immense number of combinations of hyperparameters
and input and outputs sizes, along with no precedent for recommended values,
lead us to generalize our model significantly. Although this may seem like an ability for
customizability, it severely reduces reproducability over small changes.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
